---
title: "comparison_charts"
output:
  pdf_document: default
  html_document: default
date: "2024-01-03"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(readr)
library(ggplot2)
```


```{r Import FRBUS Datasets, message=FALSE}

dynamic <- read_csv("dynamic_econ.csv", show_col_types = FALSE)
dynamic_int <- read_csv("dynamic_econ_int.csv", show_col_types = FALSE)
baseline <- read_csv("baseline_econ.csv", show_col_types = FALSE)

colnames(dynamic)[c(1)] <- c("year")
colnames(dynamic_int)[c(1)] <- c("year")
colnames(baseline)[c(1)] <- c("year")

```

```{r Import CBO dynamic score econ variables, message=FALSE}

cbo <- read_csv("cbo_dynamic_econ.csv", show_col_types = FALSE)
colnames(cbo)[c(1)] <- c("year")


```


# Tax Rates and Tax bases

### Personal Rate

```{r plot personal income tax rate}

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = TRP, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = TRP, color = "Dynamic Int")) +
  geom_line(data = baseline, aes(x = year, y = TRP, color = "Baseline"), linetype = "dashed") +
  labs(title = "Personal Income Tax Rate", x = "Year", y = "Rate") +
  scale_color_manual(values = c("Dynamic" = "blue", "Baseline" = "gray", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Corporate Rate

```{r plot Corporate tax rate}

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = TRCI, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = TRCI, color = "Dynamic Int")) +
  geom_line(data = baseline, aes(x = year, y = TRCI, color = "Baseline"), linetype = "dashed") +
  labs(title = "Corporate Tax Rate", x = "Year", y = "Rate") +
  scale_color_manual(values = c("Dynamic" = "blue", "Baseline" = "gray", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Personal tax base 

```{r plot personal income tax base}

dynamic$trp_base_delta <- (dynamic$TRP_Base/baseline$TRP_Base -1)*100
dynamic_int$trp_base_delta <- (dynamic_int$TRP_Base/baseline$TRP_Base -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = trp_base_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = trp_base_delta, color = "Dynamic Int")) +
  labs(title = "Personal Income Tax Base", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Corporate tax base 

```{r plot corporate income tax base}

dynamic$trci_base_delta <- (dynamic$TRCI_Base/baseline$TRCI_Base -1)*100
dynamic_int$trci_base_delta <- (dynamic_int$TRCI_Base/baseline$TRCI_Base -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = trci_base_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = trci_base_delta, color = "Dynamic Int")) +
  labs(title = "Corporate Tax Base", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

# Federal Government Budget variables 

### Deficit 

```{r plot government surplus}

dynamic$gfsrpn_delta <- (-dynamic$GFSRPN/-baseline$GFSRPN -1)*100
dynamic_int$gfsrpn_delta <- (-dynamic_int$GFSRPN/-baseline$GFSRPN -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = gfsrpn_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = gfsrpn_delta, color = "Dynamic Int")) +
  labs(title = "Government Deficit", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Net Transfers 

```{r plot government net transfers}

dynamic$gtn_delta <- (dynamic$GTN/baseline$GTN -1)*100
dynamic_int$gtn_delta <- (dynamic_int$GTN/baseline$GTN -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = gtn_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = gtn_delta, color = "Dynamic Int")) +
  labs(title = "Government Net Transfer Payments", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Net Interest

```{r plot government net interest}

dynamic$gfintn_delta <- (dynamic$GFINTN/baseline$GFINTN -1)*100
dynamic_int$gfintn_delta <- (dynamic_int$GFINTN/baseline$GFINTN -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = gfintn_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = gfintn_delta, color = "Dynamic Int")) +
  labs(title = "Government Net Interest Payments", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Fed Govnt Employee Comp

```{r plot government employee comp}

dynamic$egfln_delta <- (dynamic$EGFLN/baseline$EGFLN -1)*100
dynamic_int$egfln_delta <- (dynamic_int$EGFLN/baseline$EGFLN -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = egfln_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = egfln_delta, color = "Dynamic Int")) +
  labs(title = "Government Employee Comp", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Fed Govnt Expenditures

```{r plot government expen}

dynamic$egfe_delta <- (dynamic$EGFE/baseline$EGFE -1)*100
dynamic_int$egfe_delta <- (dynamic_int$EGFE/baseline$EGFE -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = egfe_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = egfe_delta, color = "Dynamic Int")) +
  labs(title = "Government Expenditures", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

# Real GDP and components 

Note in the CBO Budget and Economic Outlook Report from 2018, table B-2 reports the economic effects of the TCJA. However, the effects of TCJA on the components of real GDP are reported in units as the contribution to real GDP instead of changes relative to the baseline. So, the units in this part of the table are such that the sum of the components adds to the total effect of TCJA on real GDP.

In order to put the CBO components of real GDP numbers in the same units as we have here, I basically have just been treating the CBO components of real GDP numbers as follows (using personal consumption expenditures as an example)

$$
\text{Contribution of PCE to Difference Real GDP (reported in CBO table)} = \lambda_t \; \cdot \pi_t
$$
where $\lambda_t$ is the ratio of Real PCE to Real GDP in levels and $\pi_t$ is the percent difference in PCE post-TCJA relative to the baseline PCE. Note that $\pi_t$ is what we are trying to isolate in the graphs below. This is a very quick way to do this, but there is probably a more technically correct way. So if this sounds terribly terribly wrong, then I can adjust! 

### Real GDP 

```{r Real GDP}

dynamic$real_gdp_delta <- (dynamic$XGDP/baseline$XGDP -1)*100
dynamic_int$real_gdp_delta <- (dynamic_int$XGDP/baseline$XGDP -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = real_gdp_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = real_gdp_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = XGDP_cbo, color = "CBO"), linetype = "dashed" ) +
  labs(title = "Real GDP", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))


```

### Personal Consumption Expenditures

(Note CBO line refers to "private consumption")

```{r PCE consumption}

dynamic$cons_delta <- (dynamic$ECNIA/baseline$ECNIA -1)*100
dynamic_int$cons_delta <- (dynamic_int$ECNIA/baseline$ECNIA -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = cons_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = cons_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = ECNIA_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "Real PCE", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))


```

### Business Fixed Investment

```{r Business fixed investment}

dynamic$bfi_delta <- (dynamic$EBFI/baseline$EBFI -1)*100
dynamic_int$bfi_delta <- (dynamic_int$EBFI/baseline$EBFI -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = bfi_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = bfi_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = EBFI_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "Real Business Fixed Investment", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))


```

### Residential Investment

```{r Residential investment}

dynamic$resi_delta <- (dynamic$EH/baseline$EH -1)*100
dynamic_int$resi_delta <- (dynamic_int$EH/baseline$EH -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = resi_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = resi_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = EH_cbo, color = "CBO"), , linetype = "dashed") +
  labs(title = "Real Residential Investment", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))


```

### Imports 

```{r Imports}

dynamic$imports_delta <- (dynamic$EM/baseline$EM -1)*100
dynamic_int$imports_delta <- (dynamic_int$EM/baseline$EM -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = imports_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = imports_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = EM_cbo, color = "CBO"), , linetype = "dashed") +
  labs(title = "Real Imports", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))


```

### Exports 

```{r Exports}

dynamic$exports_delta <- (dynamic$EX/baseline$EX -1)*100
dynamic_int$exports_delta <- (dynamic_int$EX/baseline$EX -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = exports_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = exports_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = EX_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "Real Exports", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))


```

# Labor Force Variables

### LFPR 

```{r plot LFPR}

dynamic$lfpr_delta <- dynamic$LFPR - baseline$LFPR
dynamic_int$lfpr_delta <- dynamic_int$LFPR - baseline$LFPR


ggplot() +
  geom_line(data = dynamic, aes(x = year, y = lfpr_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = lfpr_delta, color = "Dynamic Int")) +
  labs(title = "LFPR", x = "Year", y = "Difference from Baseline (p.p.)") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Unemployment Rate

```{r plot u rate}

dynamic$urate_delta <- dynamic$LUR - baseline$LUR
dynamic_int$urate_delta <- dynamic_int$LUR - baseline$LUR

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = urate_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = urate_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = LUR_cbo, color = "CBO"), linetype = "dashed" ) +
  labs(title = "Unemployment Rate", x = "Year", y = "Difference from Baseline (p.p.)") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Employment

Note that CBO only reports total nonfarm payroll in their appendix B table, and the FRBUS numbers are civilian employment.

```{r plot employment}

dynamic$emp_delta <- (dynamic$LEH/baseline$LEH -1)*100
dynamic_int$emp_delta <- (dynamic_int$LEH/baseline$LEH -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = emp_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = emp_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = nonfarm_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "Employment", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```


# Inflation

### PCE Inflation

```{r plot pce inflation}

dynamic$picnia_delta <- (dynamic$PICNIA/baseline$PICNIA -1)*100
dynamic_int$picnia_delta <- (dynamic_int$PICNIA/baseline$PICNIA -1)*100

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = picnia_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = picnia_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = PICNIA_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "PCE inflation", x = "Year", y = "Percent Difference from Baseline") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

# Interest Rates

### Federal Funds Rate

```{r plot Fed funds rate}

dynamic$fedfunds_delta <- dynamic$RFF - baseline$RFF
dynamic_int$fedfunds_delta <- dynamic_int$RFF - baseline$RFF

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = fedfunds_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = fedfunds_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = RFF_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "Federal Funds Rate", x = "Year", y = "Difference from Baseline (p.p.)") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```

### Three-month treasury bill

```{r plot Three month rate}

dynamic$threemo_delta <- dynamic$RTB - baseline$RTB
dynamic_int$threemo_delta <- dynamic_int$RTB - baseline$RTB

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = threemo_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = threemo_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = RTB_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "3-Month Treasury Bill", x = "Year", y = "Difference from Baseline (p.p.)") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```


### 10-year treasury bill

```{r plot Ten year rate}

dynamic$tenyr_delta <- dynamic$RG10 - baseline$RG10
dynamic_int$tenyr_delta <- dynamic_int$RG10 - baseline$RG10

ggplot() +
  geom_line(data = dynamic, aes(x = year, y = tenyr_delta, color = "Dynamic")) +
  geom_line(data = dynamic_int, aes(x = year, y = tenyr_delta, color = "Dynamic Int")) +
  geom_line(data = cbo, aes(x = year, y = RG10_cbo, color = "CBO"), linetype = "dashed") +
  labs(title = "10-Year Treasury Note", x = "Year", y = "Difference from Baseline (p.p.)") +
  scale_color_manual(values = c("Dynamic" = "blue", "Dynamic Int" = "red", "CBO" = "black")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  scale_x_continuous(breaks = 2017:2027, labels = as.character(2017:2027))

```